---
title: "HW2"
author: "Fionnuala McPeake"
date: "September 23, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}
library(tidyverse)
#3.5.1 Question 2
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))+
  facet_grid(drv ~ cyl)

#3.5.1 Question 3
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```
The "." only produces one facet. The placement of the dot prevents a facet being placed in that orientation, if 
you look at the orientation as (parallel to x-axis ~ parallel to y-axis). 


```{r pressure, echo=FALSE}
#3.6.1 Question 6
#Graph 1
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy), se=FALSE)
#Graph 2
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy,  group = drv), se=FALSE)
#Graph 3
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = drv)) +
  geom_smooth(mapping = aes(x = displ, y = hwy,  group = drv, color = drv), se=FALSE)
#Graph 4
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = drv)) +
  geom_smooth(mapping = aes(x = displ, y = hwy), se = FALSE)
#Graph 5
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = drv)) +
  geom_smooth(mapping = aes(x = displ, y = hwy,  group = drv, linetype = drv), se=FALSE)
#Graph 6
ggplot(data = mpg, aes(x = displ, y = hwy, group = drv)) + 
  geom_point(size = 4, color = "white")+
  geom_point(aes(color = drv))


#5.2.4 Question 1
library(nycflights13)
#a
late <- filter(flights, arr_delay >= 120)
late

#b
Houston <- filter(flights, dest == "IAH" | dest == "HOU")
Houston

#c
Carrier <- filter(flights, carrier == "UA"| carrier == "AA"| carrier == "DL")
Carrier

#d
Summer <- filter(flights, month == 6 | month == 7 | month == 8)
Summer

#e
Arrive <- filter(flights, arr_delay >= 120 & dep_delay == 0)
Arrive

#f
half_hour <- filter(flights, dep_delay >= 60 & arr_delay >= 30)
half_hour

#g
Tired <- filter(flights, dep_time >= 00:00 & dep_time <= 06:00)
Tired
```

5.2.4 Q2
The "between()" helper will select everything between two limits. This could be used to find the number of 
flights that flew between the 6th and 8th months of the year in question, as well as flights that departed 
between midnight and 6am. 

```{r}
#5.2.4 Q3
sum(is.na(flights$dep_time))
sum(is.na(flights$air_time))
sum(is.na(flights$arr_time))
```
There are 9430 flights that have an "NA" input for departure time. There are 9430 flights that have flown a 
distance of "NA", and 8713 that have an "NA" for arrival time. It can be assumed that some of these flights 
are the same. This could mean that the flight was canceled.

5.2.4 Q4
NA^0 reads out of 1, which is why it is not missing. NA|TRUE is not missing because the "TRUE" part of the 
statement takes over, making the entire output "TRUE". FALSE&NA is not missing because both of these things 
cannot be true at the same time, so the expression evaluates to FALSE. 

```{r}
library(tidyverse)
LakeHuron
huron <- data.frame(year = 1875:1972, level = as.vector(LakeHuron))
ggplot(data = huron) +
  geom_line(mapping = aes(x = year, y = level, color = "blue"))+
  geom_point(mapping = aes(x = year, y = level, color = "red"), shape = 1)+
  geom_smooth(mapping = aes(x = year, y = level), se = FALSE)
```

